\documentclass[a4paper,11pt]{article}

\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{tabularx}
\usepackage[english]{babel}
\usepackage{enumitem}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section style
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\titlerule \vspace{-5pt}]
\renewcommand{\baselinestretch}{1.2}
\titlespacing*{\section}{0pt}{*3}{*3}

%-------------------------------------------
% Macros for clean content
%-------------------------------------------

\newcommand{\resumeSubheading}[4]{
  \item[]
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{#2} \\
      \multicolumn{2}{l}{\hspace{0.5em}\textit{\small #3} \hfill \textit{\small #4}} \\
    \end{tabular*}\vspace{-10pt}
}

\newcommand{\resumeItem}[2][]{%
  \if\relax\detokenize{#1}\relax
    \item \small{#2}%
  \else
    \item[] \small{#2}\vspace{#1}%
  \fi
}

\newcommand{\resumeListStart}[1][0.15in]{\begin{itemize}[leftmargin=#1,label=\textbullet]}
\newcommand{\resumeListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Omar Abdulaziz} \\ \vspace{1pt}
    \small +201007141064 $|$ 
    \href{mailto:omarabdul3ziz@gmail.com}{\underline{omarabdul3ziz@gmail.com}} $|$ 
    \href{https://linkedin.com/in/omarabdul3ziz}{\underline{linkedin.com/in/omarabdul3ziz}} $|$
    \href{https://github.com/omarabdul3ziz}{\underline{github.com/omarabdul3ziz}}
\end{center}


%-----------EXPERIENCE-----------
\section{Experience}
\resumeListStart
  \resumeSubheading
    {Software Engineer}{Oct 2021 -- Present}
    {Codescalers}{Cairo, Egypt}
    \resumeListStart[0.3in]
      \resumeItem{\textbf{Kubernetes}: Developed custom CRDs and Ingress Controllers, extending cluster functionality for scalable workloads.}
      \resumeItem{\textbf{API Development}: Delivered production-grade APIs (REST, GraphQL, RPC) strictly following OpenAPI/OpenRPC specifications, ensuring compatibility and maintainability.}
      \resumeItem{\textbf{Database Optimization}: Restructured PostgreSQL schemas, added indexes, and optimized queries, reducing API response times from 30s to 3s (10x improvement).}
      \resumeItem{\textbf{Concurrency}: Built distributed background indexers fetching and aggregating data from 3k+ nodes using Go generics and concurrency for high throughput.}
      \resumeItem{\textbf{Pub/Sub Systems}: Implemented asynchronous processing pipeline with Redis event streams, enabling reliable event-driven communication.}
      \resumeItem{\textbf{Frontend Integration}: Contributed to the dashboard (Svelte → Vue migration), integrating multiple APIs and external clients for a unified user experience.}
      \resumeItem{\textbf{DevOps \& Docker}: Created 20+ Docker images for popular DApps, showcasing deployment on in-house infrastructure and improving developer adoption.}
      \resumeItem{\textbf{Systems Programming}: Engineered low-level services leveraging Linux primitives (networking, filesystems) and extended a fetch-on-read filesystem with S3 storage wrapper.}
      \resumeItem{\textbf{Security \& Networking}: Hardened servers with NFTables-based isolation, and implemented authentication flows using OAuth and cryptographic signature verification.}
      \resumeItem{\textbf{Monitoring}: Built node monitoring services with automated health checks and caching, improving system reliability and observability.}
      \resumeItem{\textbf{Tooling \& Automation}: Developed a code-generation tool for OpenRPC specs, accelerating development and reducing boilerplate by 40\%.}
      \resumeItem{\textbf{Collaboration}: Participated in design discussions, reviewed PRs, and partnered with cross-functional teams to deliver scalable solutions and maintain quality standards.}
      \resumeItem{\textbf{Testing}: Maintained unit and integration test suites, ensuring stability and coverage across services.}
    \resumeListEnd
\resumeListEnd

\resumeListStart
  \resumeSubheading
    {Intern Software Engineer}{Aug 2021 -- Oct}
    {Codescalers}{Cairo, Egypt}
    \resumeListStart[0.3in]
      \resumeItem{\textbf{Kubernetes}: Developed custom CRDs and Ingress Controllers, extending cluster functionality for scalable workloads.}
    \resumeListEnd
\resumeListEnd

%-----------EDUCATION-----------
\section{Education}
\resumeListStart
  \resumeSubheading
    {Bachelor of Electronics and Communication Engineering}{2016 -- 2021}
    {Nile Academy}{Mansoura, Egypt}
\resumeListEnd

%-----------PROJECTS-----------
\section{Projects}
\resumeListStart
  \resumeSubheading
    {busybox.sh}{Shell}{Minimal Linux-from-scratch distribution}{}

  \resumeSubheading
    {gocker.go}{Go}{Lightweight Docker clone using Linux primitives}{}

  \resumeSubheading
    {ugit.go}{Go}{Minimal Git clone with commits and history tracking}{}

  \resumeSubheading
    {resper.go}{Python}{RESP protocol implementation (Redis wire protocol)}{}

  \resumeSubheading
    {bitcask.rs}{Rust}{Append-only key-value database based on Bitcask model}{}

  \resumeSubheading
    {process-manager.rs}{Rust}{Simple PID1 process manager for Linux}{}

  \resumeSubheading
    {tcp.c}{C}{TCP server built from scratch handling multiple connections}{}

  \resumeSubheading
    {souqnazarat}{TypeScript}{E-commerce web application}{}

  \resumeSubheading
    {roommates-finder}{TypeScript}{Platform to help users find compatible roommates}{}

  \resumeSubheading
    {irc-chat-rooms.ts}{TypeScript}{Disposable chat rooms application}{}

  \resumeSubheading
    {obsidian-toggl}{JavaScript}{Extended integration between Obsidian and Toggl for time tracking}{}

  \resumeSubheading
    {tmux-waka}{Shell}{Plugin integrating Tmux with WakaTime productivity tracking}{}

  \resumeSubheading
    {zos-pkg-manager.rs}{Rust}{Package manager for zos platform}{}

  \resumeSubheading
    {homelab}{Various}{Collection of self-hosted solutions and automation scripts}{}
\resumeListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\resumeListStart
    \resumeItem[-6pt] {\textbf{Programming Languages}{: Go, Rust, TypeScript, Shell, Python, C, SQL, Bash}} \\
    \resumeItem[-6pt] {\textbf{Databases}{: PostgreSQL, Bitcask, Redis, MongoDB}} \\
    \resumeItem[-6pt] {\textbf{Backend \& APIs}{: REST, GraphQL, RPC, Pub/Sub, gRPC}} \\
    \resumeItem[-6pt] {\textbf{Frontend}{: Vue.js, Svelte}} \\
    \resumeItem[-6pt] {\textbf{Cloud \& DevOps}{: Linux, Docker, Kubernetes, CI/CD, AWS}}
\resumeListEnd



\end{document}